The Evolution of Phenotypically Invariant Genetic Networks

### 2017-12-08 kalman_walk_paper.tex
changed title
changed title, fixed figure six Y-axis label and caption

{\centering
{\LARGE \bf Rapid speciation despite conservation of phenotype} \\ \vspace{0.5cm}
Joshua S. Schiffman$^{\dagger}$ \qquad Peter L. Ralph$^{\dagger \ddagger}$ \\ \vspace{0.5cm}
$^{\dagger}${\footnotesize {Molecular and Computational Biology, University of Southern California, Los Angeles, California 90089, U.S.A. \\
$^{\ddagger}$Departments of Mathematics and Biology \& The Institute for Ecology and Evolution, University of Oregon, Eugene, Oregon 97403, U.S.A.}} \\ \vspace{0.5cm}
{\small \texttt{jsschiff@usc.edu} \qquad 
\texttt{plr@uoregon.edu}} \\ \vspace{0.5cm}
\small \today \\
\vspace{0.25cm}
}

@@

  \begin{figure}[H]
    \centering
    %\begin{tabular}{cc}
    %\includegraphics[width=0.4\textwidth]{figures/f1_quartic2} &
    %\includegraphics[width=0.4\textwidth]{figures/f2_quad2}
    %\end{tabular}
    \includegraphics[width=0.5\textwidth]{examples/F2_vs_F1_divergence_tau0}
   % \caption{
    %\textbf{(left)} 
    \caption{Phenotype distance to optimum, $D$, using $\rho(t) = \exp(-t/4\pi)$
    for $F_1$ (black) and $F_2$ (blue) hybrids between an $A(0)$ and an $A(\epsilon)$ parent. Genetic distance is computed as 
    %Frobenius norm
    %Euclidean distance
    $\sqrt{\sum_{ij} (A_{ij}(0) - A_{ij}(\epsilon))^2}$
    %between two systems
    .}
    %\textbf{(right)} Same, but for $F_2$ offspring (one line per type of $F_2$).
    %\plri{make this $D$ not $D^2$ and say which line is the overall average $F_2$.
    %}
    \label{fig:osc_incompat}
  \end{figure}
\end{example}

>>>>

{\centering
{\Huge \bf System drift and speciation} \\ \vspace{0.75cm}
Joshua S. Schiffman$^{\dagger}$ \qquad Peter L. Ralph$^{\dagger \ddagger}$ \\ \vspace{0.5cm}
$^{\dagger}${\footnotesize {Molecular and Computational Biology, University of Southern California, Los Angeles, California 90089, U.S.A. \\
$^{\ddagger}$Departments of Mathematics and Biology \& The Institute for Ecology and Evolution, University of Oregon, Eugene, Oregon 97403, U.S.A.}} \\ \vspace{0.5cm}
{\small \texttt{jsschiff@usc.edu} \qquad 
\texttt{plr@uoregon.edu}} \\ \vspace{0.5cm}
\small \today \\
\vspace{0.25cm}
}

@@

  \begin{figure}[H]
    \centering
    %\begin{tabular}{cc}
    %\includegraphics[width=0.4\textwidth]{figures/f1_quartic2} &
    %\includegraphics[width=0.4\textwidth]{figures/f2_quad2}
    %\end{tabular}
    \includegraphics[width=0.5\textwidth]{examples/F2_vs_F1_divergence_tau0}
   % \caption{
    %\textbf{(left)} 
    \caption{Mean hybrid phenotypic distance from optimum computed with equation \ref{eqn:distance}, using $\rho(t) = \exp(-t/4\pi)$
    for $F_1$ (black) and $F_2$ (blue) hybrids between $A(0)$ and $A(\epsilon)$ parent oscillators. Genetic distance is computed as 
    %Frobenius norm
    %Euclidean distance
    $\sqrt{\sum_{ij} (A_{ij}(0) - A_{ij}(\epsilon))^2}$
    %between two systems
    .}
    %\textbf{(right)} Same, but for $F_2$ offspring (one line per type of $F_2$).
    %\plri{make this $D$ not $D^2$ and say which line is the overall average $F_2$.
    %}
    \label{fig:osc_incompat}
  \end{figure}
\end{example}
